### 2023-03-30 definitions.tex
details

Several families of formal models of processes give rise to WSTSs in a natural way, e.g. Petri nets when inclusion between markings is used as the well-ordering.

@@

@@

@@

A downard-closed set $D$ is {\em decidable} if, given $s \in S$, it is decidable whether
$s \in D$. 
%\textcolor{red}{Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.}
% \textcolor{red}{Do we still demand this ?}
%\mathieu{On peut enlever ce point de discussion ici et en discuter de manière plus complête au moment où on discute de SAFE et BAD plus en détail je pense.}

@@

\begin{theorem}(ref)
A finite basis of $ \pred^*(U)$ is computable for any effective WSTS $\mathscr{S}$ with effective pred-basis and any upward closed set $U \subseteq S$ given with its finite basis $pb(U)$.
\end{theorem}

>>>>

Several families of formal models of processes give rise to WSTSs in a natural way, e.g. Petri nets when inclusion between markings is used as the well-ordering and lossy channel systems with the subword ordering.

@@

There is a simple condition that insures that a finite basis of $\pred^*(U )$ is computable.

@@

\begin{theorem}(ref)
A finite basis of $ \pred^*(U)$ is computable for any effective WSTS $\mathscr{S}$ with effective pred-basis and any upward closed set $U \subseteq S$ given with its finite basis $B_U$.
\end{theorem}

@@

%         A downard-closed set $D$ is {\em decidable} if, given $s \in S$, it is decidable whether
%         $s \in D$.

%\textcolor{red}{Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.}
% \textcolor{red}{Do we still demand this ?}
%\mathieu{On peut enlever ce point de discussion ici et en discuter de manière plus complête au moment où on discute de SAFE et BAD plus en détail je pense.}

@@
